Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-12 WSSSPE3/report/wg_appendix_software_credit.tex
Removed large photos from repo history

The group also agreed on the fact that additional data was required to support the assertion that software was not being sufficiently cited in the literature.
In particular, this issue seemed to be field-dependent.
For example, as shown by study of Howison and Bullard~\cite{Howison2015}, in the field of biology the most-cited papers appear to be describing scientific software.
However, this may not---and likely is not---the case in other fields, nor is it clear whether developers of scientific software, even in the case of the biology field, are receiving sufficient credit for their efforts.

>>>>

The group also agreed on the fact that additional data was required to support the assertion that software was not being sufficiently cited in the literature.
In particular, this issue seemed to be field-dependent.
For example, as shown by study of Howison and Bullard~\cite{Howison2015}, in the field of biology the most-cited papers appear to be those describing scientific software.
However, this may not---and likely is not---the case in other fields, nor is it clear whether developers of scientific software, even in the case of the biology field, are receiving sufficient credit for their efforts.

During the first day of WSSSPE3 breakout sessions, the group discussed the Entertainment Identifier Registry (EIDR)\footnote{Entertainment Identifier Registry: \url{http://eidr.org}} as a potential model for scientific software.
That system assigns unique Digital Object Identifiers (DOIs)---the same system used for scientific publications---to all content (e.g., movies, television shows) and contributors, along with relevant metadata.
One important use of this system is to track rights and credit for contributors to entertainment works in order to distrubute revenues---similar to the proposed transitive credit concept.

The group also discussed separating quantitative measures (e.g., number of citations) from the value of a work in order to give credit, moving towards qualitative or anecdotal evidence of value.

PageRank for citations, based on number of mentions

market penetration or adoption rate in a community as a metric, although it was not clear how this would be measured.

Finally, the concept a software tool's uniqueness or indispensability to a community was mentioned, with value being characterized by a particular piece of software either offering unique capabilities or doing something better, faster, or with less computational requirements than other offerings.
